\begin{thebibliography}{99}

\bibitem{sketchrnn}{David Ha, Douglas Eck - \emph{A Neural Representation of 
Sketch Drawings} - 	arXiv:1704.03477, 2017}

\bibitem{quickdraw}{J. Jongejan, H. Rowley, T. Kawashima, J. Kim, and N. 
Fox-Gieg. - \emph{The Quick, Draw! - A.I. Experiment.} - \url{https://quickdraw.withgoogle.com/}, 
2016.}

\bibitem{keras}{Chollet, Fran\c{c}ois and others - \emph{Keras} - GitHub, 
\url{https://github.com/keras-team/keras}}

\bibitem{tensorflow}{Martín Abadi, Ashish Agarwal, Paul Barham, Eugene Brevdo,
Zhifeng Chen, Craig Citro, Greg S. Corrado, Andy Davis,
Jeffrey Dean, Matthieu Devin, Sanjay Ghemawat, Ian Goodfellow,
Andrew Harp, Geoffrey Irving, Michael Isard, Rafal Jozefowicz, Yangqing Jia,
Lukasz Kaiser, Manjunath Kudlur, Josh Levenberg, Dan Mané, Mike Schuster,
Rajat Monga, Sherry Moore, Derek Murray, Chris Olah, Jonathon Shlens,
Benoit Steiner, Ilya Sutskever, Kunal Talwar, Paul Tucker,
Vincent Vanhoucke, Vijay Vasudevan, Fernanda Viégas,
Oriol Vinyals, Pete Warden, Martin Wattenberg, Martin Wicke,
Yuan Yu, and Xiaoqiang Zheng. - \emph{TensorFlow: Large-scale machine 
learning on heterogeneous systems} - \url{tensorflow.org}, 2015}

\bibitem{GAN}{I. Goodfellow. - \emph{NIPS 2016 Tutorial: Generative Adversarial 
Networks.} - ArXiv e-prints, Dec. 2017.}

\bibitem{VI}{D. P. Kingma and M. Welling. - \emph{Auto-Encoding Variational Bayes.} - 
ArXiv e-prints, Dec. 2013.}

\bibitem{AR}{S. Reed, A. van den Oord, N. Kalchbrenner, S. Gómez Colmenarejo, 
Z. Wang, D. Belov, and N. de Freitas. - \emph{Parallel Multiscale Autoregressive 
Density Estimation.} - ArXiv e-prints, Mar. 2017.}

\bibitem{edward}{Dustin Tran and Alp Kucukelbir and Adji B. Dieng and Maja 
Rudolph and Dawen Liang and David M. Blei - \emph{Edward: A library for 
probabilistic modeling, inference, and criticism} - arXiv preprint arXiv:1610.09787,
 2016}

\bibitem{MDN}{Axel Brando - \emph{Mixture Density Networks (MDN) for distribution and uncertainty estimation} - \url{https://github.com/axelbrando/Mixture-Density-Networks-for-distribution-and-uncertainty-estimation/blob/master/ABrando-MDN-MasterThesis.pdf}, 2017}

\bibitem{LSTM}{Colah - \emph{Understanding lstm networks, colah's blog.} - \url{http://colah.github.io/posts/2015-08-Understanding-LSTMs/.}}

\bibitem{approx}{G. Cybenko - \emph{Approximation by Superpositions of a Sigmoidal Function} - 1989}

\end{thebibliography}